Capitalized Title Here

### 2021-03-11 CMPSpaper_writing/CMPSpaper_writing.Rmd
couple more edits

### Conceptual idea of CMPS
Once we obtain the bullet signatures, we can compare them using an algorithm that computes a similarity score. The congruent matching profile segments (CMPS) algorithm, developed by NIST for "objective comparison of striated tool marks" [@cmps], is one such algorithm. The main idea of the CMPS algorithm is that, we cut the reference profile (one of the two bullet signatures) into consecutive and non-overlapping basis segments and ask each basis segment to find the "best" registration position on the comparison profile (the other bullet signature) in terms of correlation values. Then the congruent registration position is the position where the most basis segments find it the "best", and the number of basis segments taking the congruent registration position is the CMPS score. The CMPS algorithm can assist firearm examiners with drawing a conclusion, but NIST's implementation of the CMPS algorithm was not released for the public. Thus, in this paper we present an open-source implementation of the CMPS algorithm so that everyone can use and improve it. With our implementation, one can compute the CMPS score of a comparison using the following code:

>>>>

### Conceptual idea of CMPS
\hh{Most algorithms for comparing striation marks are based on the digitized signatures XXX and produce a similarity score (some citations: chumbley score, Ganesh's fix, vorburger's ccf paper, hare).} 
 The congruent matching profile segments (CMPS) algorithm, developed by @cmps for "objective comparison of striated tool marks", is one such algorithm. The algorithm's main idea  is to take a set of consecutive and non-overlapping basis segments from  the reference profile  and  for each segment find the "best" registration position on the comparison profile (the other bullet signature) with respect to their cross-correlation values. \hh{From a comparison of these registration positions, a } **congruent registration position** is identified, and the number of basis segments taking the congruent registration position is the CMPS score. 
\hh{High CMPS scores are achieved between more similar signatures and are therefore indicative of a same-source pair. Low scores between pairs of signatures are attributed to different source pairs.} 
\hh{XXX What threshold did @cmps identify as the boundary between different source and same source? And what was the error rate in their example?}
 The CMPS algorithm can assist firearm examiners with drawing a conclusion \hh{about the source of a comparison pair}. \hh{Unfortunately, @cmps did not release any code or specific parameter settings for their implementation of the } CMPS algorithm. 
Thus, in this paper we present an open-source implementation of the CMPS algorithm \hh{in the R package CMPS available from XXX github / CRAN}. 
With our implementation, one can compute the CMPS score of a comparison using the following code:
